---
title: "RStudio Presentation with Plotly Assignment"
author: "Zhang Jinyan"
date: "08/10/2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, 
                      error = FALSE, 
                      warning = FALSE, 
                      echo = FALSE,
                      comment = NA, 
                      fig.align = 'center', 
                      dpi = 100, 
                      tidy = F, 
                      fig.path = 'fig/')
```

## Data Set

We will be using the data set from R: **airquality**.
It consists of the following variables:

* **Ozone**: Mean ozone in parts per billion
* **Solar**: Radiation: Solar radiation measured in Langleys
* **Wind**: Average win speed in miles per hour
* **Temperature**: Maximum daily temperature in degrees Fahrenheit
* **Month**: The month the measurements were taken
* **Day**: The day the measurements were taken

## Plotly Graph of Air Quality

```{r plotly-1, echo = FALSE}
library(plotly)
library(reshape2)
library(dplyr)

air <- airquality
air$Month <- factor(month.abb[air$Month], 
                    levels = c("May", "Jun", "Jul", "Aug", "Sep"))
names(air)[1:4] <- c("Ozone (parts per billion)", 
                     "Solar Radiation (Langleys)",
                     "Wind Speed (miles per hour)",
                     "Temperature (degrees F)")
                     
airMelt <- melt(data = air, id.vars = c("Day", "Month"))

g <- ggplot(data = airMelt,
            aes(x = Month, y = value))
g <- g + geom_boxplot(na.rm = TRUE,
                      aes(fill = Month)) +
      facet_wrap(~ variable) +
      scale_fill_brewer(palette = "Accent") +
      labs(x = "", y = "")

ggplotly(g)
```

